Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-05-08 manuscript/manuscript.tex
updated section on approx diversity reduction

In the linked selection literature, it is common to translate the impact of
linked selection as a reduction in the background level of neutral pairwise
diversity, $\pi_0$. Under the coalescent, $\pi = 2 \mu \E(T_2)$ where $\E(T_2)$
is the pairwise time to coalescence, which under drift alone in a constant
population of size $N$, is $\E(T_2) = 2N$.

>>>>

In the linked selection literature, it is common to translate the impact of
linked selection as a reduction in the level of neutral pairwise diversity in
the absence of linked selection, $\pi_0$. Under the coalescent, $\pi_0 = 2 \mu
\E(T_2)$ where $\E(T_2)$ is the pairwise time to coalescence, which under drift
alone in a constant population of size $N$, is $\E(T_2) = 2N$. The fraction of
neutral diversity (in the absence of linked selection) reduced by selection is
then, $1 - \nicefrac{\bar{\pi}}{\pi_0}$, or equivalently, $1 -
\nicefrac{N_e}{N_{e,D}}$. Then,

\begin{align}
  G(t) \lesssim 1 - \frac{N_e}{N_{e,D}} 
\end{align}

which shows that our measure $G(t)$ is a lower bound, over much shorter
timescales, to the familiar measure $1 - \nicefrac{\bar{\pi}}{\pi}$.

Using another approximation, we can consider what roughly equivalently
reduction in diversity due to background selection is expected, using the
theory of \textcite{Hudson1994-oh,Hudson1995-xc}. Their theory states,

\begin{align}
  \frac{N_e}{N_{e,D}} = \exp\left(-\frac{U}{R}\right)
\end{align}

where $U$ is the total genome-wide deleterious mutation rate per generation,
and $R$ is the total recombination map length in Morgans. For \emph{Drosophila
melanogaster} (we currently lack good estimates for \emph{D. simulans}), $R
\approx 3$ Morgans, implying a $G(t)$ of at least 20\% implies $U \gtrsim
0.67$. This is entirely consistent with recent work estimating $U \approx 1.6$
in \emph{D. melanogaster} from longer timescale population genetic data
\parencite{Elyashiv2016-vt} (their estimate of $U$ implies a $G(t) \approx
0.59$, or around 59\% reduction in neutral diversity).
